%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder} % Affiliation/role
    {Project Cognoma} % Organization/group
    {Philadelphia, PA} % Location
    {June 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Co-founded philanthropic working group in center city,
               Philadelphia - http://cognoma.org.}
        \item {Established purpose to put machine learning in the hands of
               cancer biologists.}
        \item {Facilitated initial research and development to provide the
               foundation of the web-app purpose.}
        \item {Provide support to new organization members and guide research
               questions and UI/UX decisions.}
      \end{cvitems}
    }

  \cventry
    {Research Scientist} % Job title
    {Morphotek Inc.} % Organization
    {Exton, PA} % Location
    {May 2014 - July 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed a three month internship learning molecular biology
               research skills and study design.}
        \item {Conducted various cellular biotechniques including cell culture,
               cellular killing assays, and flow cytometry.}
        \item {Collaborated with Antibody Development Team to assess efficacy
               of antibodies in killing cancer cell lines.}
      \end{cvitems}
    }

  \cventry
    {Website Manager} % Job title
    {Samzies Uniforms} % Organization
    {Ewing, NJ} % Location
    {Feb 2011 - Aug 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed sales and project development of a new online store
               specializing in police, fire, and EMT uniforms.}
        \item {Analyzed web traffic to develop more effective sales promotions
               and search engine optimization.}
        \item {Troubleshot all network, computer, and general technology
               problems.}
      \end{cvitems}
    }
\end{cventries}
