%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

  \cvskill
    {2017} % Category
    {\textbf{Way, G.P.}, Allaway, R.J., Bouley, S.J., Fadul, C.E., Sanchez, Y.,
    Greene, C.S. \textit{A machine learning classifier trained on cancer
    transcriptomes detects NF1 inactivation signal in glioblastoma.}
    \textsc{BMC Genomics.} https://doi.org/0.1101/075382.}

    \cvskill
    {2017} % Category
    {\textbf{Way, G.P.}, Youngstrom, D.W., Hankenson, K.D., Greene, C.S., Grant,
    S.F.A. \textit{Discovering candidate genes from GWAS signals using
    topologically associating domains}
    \textsc{BioRxiv Preprint.} https://doi.org/10.1101/087718.}

    \cvskill
    {2016} % Category
    {\textbf{Way, G.P.}, Rudd, J., Wang, C., Hamidi, H., Fidley, B.L., Konecny,
    G.E., Goode, E.L., Greene, C.S., Doherty, J.A. \textit{Cross-population
    analysis of high-grade serous ovarian cancer reveals only two robust
    subtypes.} \textsc{G3: Genes | Genomes | Genetics.}
    https://doi.org/10.1534/g3.116.033514.}

    \cvskill
    {2016} % Category
    {\textbf{Way, G.P.}, Southwell, M., McRobert, S. \textit{Boldness,
    aggression, and shoaling assays for zebrafish behavioral syndromes.}
    \textsc{Journal of Visualized Experiments.} https://doi.org/10.3791/54049.}

    \cvskill
    {2015} % Category
    {\textbf{Way, G.P}, Ruhl, N., Snekser, J., Kiesel, A., McRobert, S.
    \textit{A comparison of methodologies to test aggression in zebrafish.}
    \textsc{Zebrafish.} https://doi.org/10.1089/zeb.2014.1025.}

    \cvskill
    {2015} % Category
    {Moss, S., Tittaferrante, S., \textbf{Way, G.P.}, Fuller, A., Sullivan, N.,
    Ruhl, N., McRobert, S. \textit{Interactions between aggression, boldness
    and shoaling in juvenile convict cichlid kin.} \textsc{Behavioural
    Processes.} https://doi.org/10.1016/j.beproc.2015.10.012.}

    \cvskill
    {2015} % Category
    {\textbf{Way, G.P.}, Kiesel, A., Snekser, J., Ruhl, N and McRobert, S.P.
    \textit{Sex differences in a shoaling-boldness behavioral syndrome, but no
    link with aggression.}
    \textsc{Behavioural Processes.}
    https://doi.org/10.1016/j.beproc.2014.12.014.}

\end{cvskills}
