%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Program}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {University of Pennsylvania} % Job title
    {Using Deep Learning to Detect Gene Expression-Based Cellular States}
    {Philadelphia, PA} % Location
    {Dec 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing state-of-the-art deep learning models in the genomics
               domain.}
        \item {Building a generative adversarial net framework to identify
               stable cellular states}
        \item {Extending application for use with high-throughput FISH, RNAseq,
               and single cell RNAseq data.}
        \item {Identifying latent space of cellular activity to determine how
               aberrant genomic events and treatments shape tumor landscapes.}
      \end{cvitems}
    }

  \cventry
    {University of Pennsylvania} % Job title
    {Machine Learning Classification of NF1 Status in Glioblastoma}
    {Philadelphia, PA} % Location
    {Aug 2015 - Jan 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed research strategy and computational pipeline.}
        \item {Trained logistic regression classifiers to detect when a brain
               tumor has inactivated NF1.}
        \item {Gained ability to detect ``hidden responders'' who may benefit
               from small molecule targetted treatment.}
        \item {Extending framework within The Cancer Genome Atlas consortium
               to detect other gene inactivation signatures.}
      \end{cvitems}
    }

  \cventry
    {University of Pennsylvania} % Job title
    {High-Grade Serous Ovarian Cancer Subtypes} % Organization
    {Philadelphia, PA} % Location
    {Sept 2014 - Oct 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed research strategy and computational pipeline.}
        \item {Identified two robust subtypes that may inform treatments.}
        \item {Collaborated with UCLA and Mayo clinic to deposit 528 additional
              tumors to gene expression databases.}
        \item {Contributed several poster and oral presentations and
               publications.}
      \end{cvitems}
    }

\end{cventries}
